---
title: "5.0 Modeling Viz Functions"
output: html_notebook
---

# Modeling Functions

This documnet contains 4 functions that are used heavily in the modeling process. The first is a function that synthesizes the model output and the later ones are

The goal is that you can essentially treat this as package, and just run this once, and then . Each of the visualization functions outputs a ggplot obejct that can be modified just like any other ggplot object (by adding layers etc.). See other files for example usage

## (func-def) Tidy Tobit Model
This function takes in an output object from the `AER::tobit` function and returns it as a tidy-table with all the necessary elements for exporting and piping into the later steps of the process (analysis, tuning and visualization)

```{r tidy-tobit-model}
tidy_tobit_model <- function(model, print=F) {
  tidy_model <- summary(model)$coefficients %>% broom::tidy()
  
  tidy_model$term_name <- vars_to_include[tidy_model$term]
  
  tidy_model_clean <- tidy_model %>% 
    select(v = term, term = term_name, everything()) %>%
    separate(term, into = c('Term', 'Value'), sep = NAMES_SEP)
  
  if(print) {
    tidy_model_clean %>%
      print(n = 43)
  }
  
  return(tidy_model_clean)
}
```


## (func-def) plot_vif 
```{r function plot vif}
plot_vif <- function(pltdf, title=NA, remove_group_name = TRUE) {
  df.plt <- pltdf
  
  if(remove_group_name) 
    df.plt$Term <- strsplit(df.plt$Term, ':') %>% sapply(tail, 1)
      
  plt <- df.plt %>%
    ggplot(aes(x     = vif, 
               y     = fct_rev(as_factor(Term)), 
               label = signif_stars,
               fill  = factor(signif_level),
               group = fct_rev(grp)
               # label = scales::number(p.value, accuracy = .0001)
             )) + 
             #label = paste0(p.value, ': ', signif))) +
  geom_bar(stat='identity', color = 'grey64') +
  #geom_text(nudge_x = .65, nudge_y = 0) + #-.25) + 
  geom_text(size = 6, nudge_x = .55, nudge_y = -.25) + 
  scale_fill_manual(values = set_names(
      c(colorRampPalette(c('#efefef', 'dodgerblue3'))(4), 'dodgerblue4'), 
      rev(paste0('<' , tail(p_cutpoints, -1))))) + 
  guides(fill = guide_legend(reverse=T)) + 
  labs(
    title = title,
    x = 'Variance Inflation',
    y = NULL,
    fill = 'Signif.\n Level'
  ) + 
  facet_grid(grp~., scales='free', space='free_y', switch='y') + 
  theme(
    strip.placement = 'outside',
    strip.clip='off',
    panel.spacing = unit(0, 'in'), 
    panel.border = element_rect(color='gray33', fill=NA, linetype=1)#,
    #panel.grid.major = element_blank()
  )
  
  plt
}
```

## (func-def) plot_corrpplot
```{r function plot corrplot}
# Function
plot_corrplot <- function(pltdf, vars_named, title='CorrPlot') {
  pltdf %>%
  select(!!!vars_named) %>%
  cor() %>%
  ggcorrplot::ggcorrplot(
    lab = TRUE, lab_size = 3.5,
    show.diag = FALSE,
    title = title
  )
}
```

## (func-def) plot_regression_coefs
```{r function plot regression coefs}
# Make Regression Plot
plot_regression_coefs <- function(plotdf, title = NULL, hide_nonprimary_grps = FALSE, primary_grps = c('Built-Env.'), remove_missing_flags=FALSE, display_summaries=FALSE, remove_group_name=TRUE, add_labels=FALSE, missing_red=TRUE, add_column_headers=TRUE,
                                  add_demarcation_lines=TRUE, demarcation_offset=13) {
  df.plt <- plotdf %>%
    mutate(hide = (grp %in% primary_grps)) %>%
    arrange(grp)
  
  # Hide groups (usually to display only the ones we care about.)
  ## Modify 'hide' column to do this
  if(hide_nonprimary_grps)
    df.plt <- df.plt %>% 
      filter(hide)
  
  # Remove the group name before the colon
  if(remove_group_name) 
    df.plt$Term <- strsplit(df.plt$Term, ':') %>% 
      sapply(tail, 1) %>% 
      str_trim() %>%
      str_replace('Missing', '[Missing]')
  
  # Remove all Missing values
  if(remove_missing_flags)
    df.plt <- df.plt %>%
      filter(Term != '[Missing]')
  
  if(display_summaries) {
    df.plt$Term <- paste0(df.plt$Term, '\n(',
          'µ: ', scales::number(df.plt$mean, accuracy=.01), 
          '  σ: ', scales::number(df.plt$sd, accuracy=.01),
          ')')
  }
  
  # Create separate factor version of Terem and move 'Missing' to end
  df.plt$Term_display <- df.plt$Term %>% 
    as_factor() %>% 
    fct_relevel('[Missing]', after = Inf) %>% 
    fct_rev()
  #df.plt$Term_display <- fct_recode(df.plt$Term_display, 'Missing', '[Missing]')
  
  # Color "Missing' as red --> This doesn't work
  y_axis_colors <- 'black'
  if(missing_red) {
    y_axis_colors <- ifelse(str_detect(df.plt$Term_display, 'Missing$'), 'firebrick3', 'black')
  }
  
  # Default Val
  if('default_val' %notin% names(df.plt))
    df.plt$default_val <- NA
  
  # Find max coef for even axes
  max_coef <- max(abs(df.plt$estimate))
  
  # Function to format facets
  n_grps <- length(unique(plotdf$grp)) + if_else(add_column_headers, 1, 0)
  facet_formatter <- function(x) {
      if((add_column_headers) && (x %% n_grps == 1)) {
        # this is for the colun headers
        element_text(size = 14, face='bold')
      } else if(x <= n_grps) {
        # First Column (Group)
        element_text(size=13) 
      } else if(x <= 2*n_grps)  {
        # Second Column (Base Value) 
        element_text(size=10, color='firebrick2')
      }
  }
  
  # Add Column Headers
  if(add_column_headers) {
    table_header_row <- tibble(grp = 'Group', default_val = 'Base Value', Term = NA, estimate = 0, signif_stars = noquote(''), signif_level = noquote('<1)'))
    df.plt <- bind_rows(table_header_row, df.plt) %>% mutate(grp = fct_inorder(grp))
  }
  
  plt <- df.plt %>%
    ggplot(aes(
      y = Term_display, 
      x = estimate, 
      fill = factor(signif_level), group = fct_rev(grp),
      label = signs::signs(estimate, add_plusses = TRUE, format = scales::number_format(accuracy=.001))
    )) + 
    geom_bar(stat = 'identity', color = 'grey64') + 
    scale_fill_manual(values = set_names(
      c(colorRampPalette(c('#efefef', 'dodgerblue3'))(4), 'dodgerblue4'), 
      rev(paste0('<' , tail(p_cutpoints, -1)))))  + 
    labs(
      x = 'Coefficient Estimate\n(Δ vmt)',
      y = NULL,
      #y = 'Variable',
      fill = 'Signif.\n Level',
      title = title,
      color = paste0('Signif at ', ALPHA, ' level')
    ) + 
    guides(fill = guide_legend(reverse=T)) + 
    scale_x_continuous(breaks = scales::breaks_width(5), 
                       minor_breaks = scales::breaks_width(1), 
                       limits = c(-max_coef, max_coef),
                       labels = signs::signs_format(add_plusses=TRUE)) + 
    theme(
      title = element_text(size = 15),
      strip.placement = 'outside',
      strip.clip='off',
      strip.switch.pad.wrap = unit(1,'in'),
      strip.text.y.left = element_text(angle=0, hjust=0),
      strip.background.y = element_rect(color='grey33', linewidth=.33),
      panel.spacing.y = unit(.05, 'in'), 
      panel.border = element_rect(color='gray33', fill=NA, linetype=1,linewidth = unit(.5, 'in')),
      #axis.text.y.left = element_text(color = c('Missing'='red', 'Other'='black'))
  ) +
    ggh4x::facet_grid2(
    #facet_grid(
      grp+default_val~., 
      scales='free', space='free_y', switch='y', 
      labeller = label_value, 
      #axes = 'y', 
      strip=ggh4x::strip_themed(
        text_y = lapply(1:(n_grps * 2), facet_formatter)
      )
    )
  
  # Add labels
  if(add_labels) {
    plt <- plt + 
      geom_label(fill = '#efefef')
  }
    
  # Add demarcation lines
  if(add_demarcation_lines) {
    plt <- plt + 
      coord_cartesian(clip = 'off') + 
      annotation_custom(grob = grid::linesGrob(), xmin = -max_coef - demarcation_offset, xmax = -max_coef + 5, ymin = .4, ymax = .4) + 
      annotation_custom(grob = grid::linesGrob(), xmin = -max_coef - demarcation_offset, xmax = max_coef, ymin = .055, ymax = .055)
  }
  #plt <- plt
    
  plt
}
```