---
title: "CARB Project Modeling (1.0)"
subtitle: 'Background'
output: html_notebook
editor_options: 
  chunk_output_type: console
---

# Intro
This is modeling for the CARB AHSC Analysis Project.
We are starting from scratch for clarity and so that it can be replicated in the future.

```{r env}
library(tidyverse)
```

# Data Load/Exploration
```{r Load Data Update}
data.v6 <- read_csv('data/DataforExport_V6.csv')
data.v6 %>% names() %>%
  sapply(function(x) x %in% names(data.bak)) %>%
  summary()

# Add rownumbers as id
data.v6 <- data.v6 %>% 
  mutate(id = row_number()) %>% 
  select(id, everything())

# Load CBSA dictionary for future use
cbsa_codes <- read_csv('../data/cbsa2fipsxw.csv')
cbsa_code_dict <- cbsa_codes %>% distinct(cbsacode, cbsatitle)

# create new dataframe
df.clean <- tibble(data.frame(id = data$id, vmt = data$daily_vmt, veh_trips = data$num_privatevehicle_trips))
df.clean
````


Define DVs
```{r}
# We're most likely gonna just use `daily_vmt`, but could to have
dvs <- c(
  'daily_vmt', 
  'num_trips', 
  'num_privatevehicle_trips', 
  'num_publictransit_trips', 
  'num_walk_trips', 
  'num_bike_trips', 
  'walk_trip_dist', 
  'walk_trip_dur'
)

dv <- dv[1]

```

# Data Assembly/Cleaning

## Demos - Standard Columns (Clean)

### `HH_Income`
```{r clean HH_Income}
# `hhincome_updated`
data$hhincome_updated %>% unique()
# data %>% select(!!var_list)

# Let's prepend a _ to the ones that need it 
income_dictionary <- 
  c(
  '1: Less than $10,000'    = '01: $00_to_09k',
  '2: $10,000 to $14,999'   = '02: $10_to_14k',
  '3: $15,000 to $24,999'   = '03: $15_to_24k',
  '4: $25,000 to $34,999'   = '04: $25_to_34k',
  '5: $35,000 to $49,999'   = '05: $35_to_49k',
  '6: $50,000 to $74,999'   = '06: $50_to_74k',
  '7: $75,000 to $99,999'   = '07: $75_to_99k',
  '8: $100,000 to $124,999' = '08: $100_to_124k',
  '9: $125,000 to $149,999' = '09: $125_to_149k',
  '10:$150,000 to $199,999' = '10: $150_to_199k',
  '11: $200,000 or more'    = '11: $200k_and_up',
  '12: Missing Data'        = '12: Missing Data'
  )

## Assign Income Cats
df.clean$hhincome_cat <- income_dictionary[data$hhincome_updated]

## Factorize
# str_split_fixed(df.clean$hhincome_cat, ':', 2)[,1] %>% as.numeric()

df.clean$hhincome_cat <- factor(df.clean$hhincome_cat, levels=df.clean$hhincome_cat %>% unique() %>% sort())

# Value

levels(df.clean$hhincome_cat)
income_valuation <- 
  c(
      '01' = 5,
      '02' = 12.5,
      '03' = 20,
      '04' = 30,
      '05' = 42.5,
      '06' = 62.5,
      '07' = 87.5,
      '08' = 112.5,
      '09' = 137.5,
      '10' = 175,
      '11' = 250,
      '12' = NA
    )

## Assign
df.clean$hhincome_est <- income_valuation[substr(df.clean$hhincome_cat, 1, 2)]

## Check

n_total <- nrow(df.clean)

df.clean %>%
  group_by(hhincome_cat, hhincome_est) %>%
  summarize(n = n(), `%` = n()/n_total)

df.clean %>%
  group_by(hhincome_cat) %>%
  summarize(mean_est = mean(hhincome_est), n = n(), `%` = n()/n_total)

```

#### `HH_income` - Open-ended
```{r income-OE}
df.clean$hhincome_OE___NotMissing <- (df.clean$hhincome_cat != '12: Missing Data') %>% as.numeric()   # `as.numeric` just turns TRUE/FALSE
df.clean$hhincome_OE____10k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 10) %>% as.numeric()
df.clean$hhincome_OE____15k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 15) %>% as.numeric()
df.clean$hhincome_OE____25k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 25) %>% as.numeric()
df.clean$hhincome_OE____35k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 35) %>% as.numeric()
df.clean$hhincome_OE____50k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 50) %>% as.numeric()
df.clean$hhincome_OE____75k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 75) %>% as.numeric()
df.clean$hhincome_OE___100k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 100) %>% as.numeric()
df.clean$hhincome_OE___125k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 125) %>% as.numeric()
df.clean$hhincome_OE___150k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 150) %>% as.numeric()
df.clean$hhincome_OE___200k_and_up <- if_else(as.numeric(df.clean$hhincome_cat) == 12, 0, df.clean$hhincome_est > 200) %>% as.numeric()

df.clean %>% 
  select(starts_with('hhincome_OE')) %>%
  rename_with(\(x) str_replace(x, 'hhincome_OE___', '')) %>%
  summarize(across(everything(), 
                   .fns = c(n = \(x) sum(x, na.rm = T), 
                            n_NA = \(x) sum(is.na(x))), 
                   .names = '{.col}___{.fn}')) %>% 
  pivot_longer(everything()) %>%
  separate(name, into = c('col', 'metric'), sep = '___') %>%
  pivot_wider(names_from = 'metric')
```

### `Age`
```{r clean Age}
# Age - un-dummify
## First confirm, all only add to 1
data %>% 
  select(starts_with('age_')) %>%
  mutate(sum = rowSums(across(where(is.numeric)))) %>%
  filter(sum != 1) # 119 people don't have age

age_buckets <- 
  data %>% 
  select(id, starts_with('age_')) %>%
  pivot_longer(cols=-id) %>%
  filter(value == 1) %>%
  mutate(name = str_replace(name, 'age_', '')) %>%
  select(id, bucket = name)

df.clean$age_bucket <- 
  data %>% 
  left_join(
    age_buckets,
    by = 'id'
  ) %>%
  pull(bucket)


# Age Bucket rename
df.clean$age_bucket %>% unique()
df.clean$age_bucket <- df.clean$age_bucket %>% replace_na('Missing')
df.clean$age_bucket %>% unique()
age_bucket_dictionary <- c(
  "under_5" = '00_to_04',
  "5_to_14"     = '05_to_14',
  "15_to_24"    = '15_to_24',
  "25_to_34"    = '25_to_34',
  "35_to_44"    = '35_to_44',
  "45_to_54"    = '45_to_54',
  "55_to_64"    = '55_to_64',
  "65_to_74"    = '65_to_74',
  "75_and_above"   = '75_and_up',
  'Missing'     = 'Missing'
)

## Assign new dictionary
df.clean$age_bucket <- age_bucket_dictionary[df.clean$age_bucket]

## Check
df.clean$age_bucket %>% unique() %>% sort()

## Factorize - we need to factorize so the open-ended buckets will work
df.clean$age_bucket <- factor(df.clean$age_bucket, levels = sort(unique(df.clean$age_bucket)))

# Value
age_valuation <-
  c(
    '00_05' = 3,
    '05_14' = 10,
    '15_24' = 20,
    '25_34' = 30,
    '35_44' = 40,
    '45_54' = 50,
    '55_64' = 60,
    '65_74' = 70,
    '75_and_up' = 82,
    'Missing' = NA,
    NA
  )

## Assign Valuation
df.clean$age_est <- age_valuation[df.clean$age_bucket]

## Checks
df.clean %>%
  group_by(age_bucket, age_est) %>%
  summarize(n = n(), `%` = n()/n_total)

df.clean %>%
  group_by(age_bucket) %>%
  summarize(mean(age_est)) # perfect
```

#### Age - Open-ended
```{r age-OE}
# Open Ended - here
df.clean$age_OE___NotMissing <- (df.clean$age_bucket != 'Missing') %>% as.numeric() # `as.numeric` just turns TRUE/FALSE into 1/0
df.clean$age_OE___15_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 15))
df.clean$age_OE___25_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 25))
df.clean$age_OE___35_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 35))
df.clean$age_OE___45_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 45))
df.clean$age_OE___55_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 55))
df.clean$age_OE___65_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 65))
df.clean$age_OE___75_and_up <- if_else(df.clean$age_bucket == 'Missing', 0, as.numeric(df.clean$age_est > 75))

df.clean %>% 
  select(starts_with('age_OE')) %>%
  rename_with(\(x) str_replace(x, 'age_OE___', '')) %>%
  summarize(across(everything(), .fns = c(n = \(x) sum(x, na.rm = T), n_NA = \(x) sum(is.na(x))), .names = '{.col}___{.fn}')) %>% 
  pivot_longer(everything()) %>%
  separate(name, into = c('col', 'metric'), sep = '___') %>%
  pivot_wider(names_from = 'metric')
  
```

### `Education`
```{r clean Education}
# Education
data$educ_updated %>% unique()
education_dictionary <- c(
  "Less than a high school graduate" = 'LessThanHS',
  "High school graduate or GED" = 'HighSchool',
  "Some college or associates degree" = 'SomeCollege',
  "Bachelor's degree" = 'Bachelors',
  "Graduate degree or professional degree" = 'Graduate',
  "Missing Data" = 'Missing'
)
df.clean$education <- education_dictionary[data$educ_updated]

df.clean %>%
  group_by(education) %>%
  summarize(n = n(), `%` = n()/n_total)

## Factorize 
df.clean$education <- factor(df.clean$education, levels = c('LessThanHS', 'HighSchool', 'SomeCollege', 'Bachelors', 'Graduate', 'Missing'))

levels(df.clean$education)
```

#### `Education` - Open-ended
```{r education-OE}
# See previous examples of `Open-Ended` for explanation
df.clean$education_OE___NotMissing <- (df.clean$education != 'Missing') %>% as.numeric()
df.clean$education_OE___HighSchool_and_up <- if_else(df.clean$education == 'Missing', 0, as.numeric(df.clean$education) > 1)
df.clean$education_OE___SomeCollege_and_up <- if_else(df.clean$education == 'Missing', 0, as.numeric(df.clean$education) > 2)
df.clean$education_OE___Bachelors_and_up <- if_else(df.clean$education == 'Missing', 0, as.numeric(df.clean$education) > 3)
df.clean$education_OE___Graduate_and_up <- if_else(df.clean$education == 'Missing', 0, as.numeric(df.clean$education) > 4)

# Test Output of the transformation
df.clean %>% 
  select(starts_with('education_OE')) %>%
  rename_with(\(x) str_replace(x, 'education_OE___', '')) %>%
  summarize(across(everything(), .fns = c(n = \(x) sum(x, na.rm = T), n_NA = \(x) sum(is.na(x))), .names = '{.col}___{.fn}')) %>% 
  pivot_longer(everything()) %>%
  separate(name, into = c('col', 'metric'), sep = '___') %>%
  pivot_wider(names_from = 'metric')
  
```

### `Race`
```{r clean Race}
# Race
race_dictionary <- c(
  'Some other race' = 'Other',
  'Native Hawaiian or other Pacific Islander' = 'PI',
  'American Indian or Alaska Native' = 'AI',
  'Black or African American' = 'AfAm',
  'Missing Data' = 'Missing',
  'Multiple responses selected' = 'Multi',
  'Asian' = 'Asian',
  'White' = 'White'
)

df.clean$race <- race_dictionary[data$race_updated]

## Checks
df.clean$race %>% 
  table()

## Consolidated
race_dictionary.consolidated <- c(
  'Some other race' = 'AI_Other_Multiple',
  'Native Hawaiian or other Pacific Islander' = 'AAPI',
  'American Indian or Alaska Native' = 'AI_Other_Multiple',
  'Black or African American' = 'AfAm',
  'Missing Data' = 'Missing',
  'Multiple responses selected' = 'AI_Other_Multiple',
  'Asian' = 'AAPI',
  'White' = 'White'
)

## Race Assigned
df.clean$race_consolidated <- race_dictionary.consolidated[data$race_updated]
df.clean$race_consolidated %>% table()

df.clean %>%
  group_by(race, race_consolidated) %>%
  summarize(n = n(), `%` = n()/n_total)
```
Here we can combine the lower frequency races. We should have ethnicity somewhere??

### `Sex`/`Homeown`/`HH_size`
```{r other}
# Addditional remove spaces
df.clean$homeown <- 
  data$homeown_updated %>% 
  str_replace_all('Missing Data', 'Missing') %>%
  str_replace_all('Error', 'Missing')

df.clean$sex <- str_replace_all(data$sex_updated, 'Missing Data', 'Missing')

# Consolidation
df.clean$sex
df.clean$sex_consolidated <- if_else(df.clean$sex == 'Male', 'Male', 'Not_Male')
df.clean %>% 
  group_by(sex, sex_consolidated) %>%
  summarize(n = n(), `%` = n()/n_total)

df.clean$hhsize <- data$hhsize_updated
```

### `Youngchild`, `hhsize`
```{r clean-other}
data %>% names() %>% paste0(collapse='\n') %>% cat() # youngchild_updated, hh_cbsa_updated
df.clean$youngchildren <- data$youngchild_updated

count(data, hhsize_updated)
```

## Built-Environment Columns (Assembly)

### Rename Cols
```{r built-enviornment col assembly}
names(data) %>% paste0(collapse='\n') %>% cat()

BE_suffixes <- c('bg','half','one','two')

data %>%
  select(ends_with('bg')) %>%
  names()
  #select(ends_with(BE_suffixes))

data %>%
  select(starts_with('NumBusStops'))


# Fix columns names
data <-
  data %>%
  rename(
    StreetDens_OX24_two   = StreetDens_OX24_two_updated,
    NetLoadDens_OX24_two  = NetLoadDens_OX24_two_updated,
    JobsWithin45_Car      = JobsWithin45_Car_2,
    JobsWithin45_Transit   = JobsWithin45_Transit_3,
    distrail_car_raw       = Car_DistToRail,
    distrail_walk_raw      = Walk_DistToRail,
    distrail_car_eighth    = distrail_eighthmi_car, 
    distrail_car_quarter   = distrail_quartmi_car, 
    distrail_car_3eighth   = distrail_3eighthmi_car, 
    distrail_car_half      = distrail_halfmi_car, 
    distrail_car_3quarter  = distrail_3quartmi_car, 
    distrail_car_one       = distrail_onemi_car, 
    distrail_car_far       = distrail_far_car, 
    distrail_walk_eighth   = distrail_eighthmi_walk, 
    distrail_walk_quarter  = distrail_quartmi_walk, 
    distrail_walk_3eighth  = distrail_3eighthmi_walk, 
    distrail_walk_half     = distrail_halfmi_walk, 
    distrail_walk_3quarter = distrail_3quartmi_walk, 
    distrail_walk_one      = distrail_onemi_walk,
    distrail_walk_far      = distrail_far_walk,
    # NumBusStops_bg         = NumBusStops_bg, 
    NumBusStops_quarter    = NumBusStops_quartmi,
    NumBusStops_3eighth    = NumBusStops_3eighthmi,
    NumBusStops_half       = NumBusStops_halfmi,
    NumBusStops_one        = NumBusStops_onemi
  )
```

### Standard BE Cols
These are the BE cols with the standard suffixes
```{r}
BE_cols.std <- c(
  'PopDens',
  # Attraction Density
  'EmpDens', 
  'RetDens', 'EntDens', 'IndDens', 
  'OffDens', 'SvcDens', 'HlthDens', 'EduDens', 'PubDens', 
  # Job Wage Categories
  #'LowWage', 'MedWage', 'HiWage',
  # Street Network
  'StreetDens_GF18','StreetDens_OX24', 'Missing_StreetDens_OX24',
  'IntersectionDens_OX24', 'Missing_IntersectionDens_OX24',
  'NetLoadDens_GF18', 'NetLoadDens_OX24'
)



# Thousand Columns
data %>% select(ends_with('thous')) # So just `PopDens` and `EmpDens`

# Check in on columns that haven't been yet used
names(data)[!names(data) %>% sapply(\(x) (x %in% c(
  names(df.clean),
  data %>% select(starts_with('age')) %>% names(),
  data %>% select(starts_with('educ')) %>% names(),
  data %>% select(ends_with('updated')) %>% names(),
  data %>% select(ends_with('thous')) %>% names(),
  data %>% select(starts_with('Missing')) %>% names(),
  # "race_updated", "sex_updated", "age_under_5", "age_5_to_14", "age_15_to_24", "age_25_to_34", "age_35_to_44", "age_45_to_54", "age_55_to_64", "age_65_to_74", "age_75_and_above", "educ_updated", 
  # 'educ_HS_above', 'educ_AA_above', 'educ_BA_above', 'educ_MS_above',
  # 'hh_cbsa_name', 'hhsize_updated', 'hhincome_updated', 'homeown_updated', 'youngchild_updated',
  do.call(paste, c(expand.grid(BE_cols.std, BE_suffixes), sep='_'))
)))] %>% 
  paste0(collapse = "', \n'") %>% 
  cat()

# Add to df.clean
missing_cols <- c()
for(c in BE_cols.std) {
  for(s in BE_suffixes) {
    colname <- paste0(c, '_', s)
    if(colname %in% names(data)) {
      df.clean[colname] <- data[colname]
    } else {
      cat(paste(colname, 'Missing\n'))
      missing_cols <- c(missing_cols, colname)
    }
  }
}

missing_cols
```

### Other BE Cols
```{r BE_cols.other}
data %>% select(starts_with('distrail')) %>% names() %>% paste0(collapse = "', '")
BE_cols.other <- c(
  # Job Accessibility
  'JobsWithin45_Car', 
  'JobsWithin45_Transit',
  # Distrail - Raw
  'distrail_car_raw',
  'distrail_walk_raw', 
  # Distrail - Car
  'distrail_car_eighth', 
  'distrail_car_quarter', 
  'distrail_car_3eighth', 
  'distrail_car_half', 
  'distrail_car_3quarter', 
  'distrail_car_one', 
  'distrail_car_far', 
  # Distrail - Walk
  'distrail_walk_eighth', 
  'distrail_walk_quarter', 
  'distrail_walk_3eighth', 
  'distrail_walk_half', 
  'distrail_walk_3quarter', 
  'distrail_walk_one',
  'distrail_walk_far', 
  # Num Bus Stops
  'NumBusStops_bg',
  'NumBusStops_quarter',
  'NumBusStops_3eighth',
  'NumBusStops_half',
  'NumBusStops_one',
  # Bus Stop Density
  'BusStopDens_bg'
)

names(data)[!sapply(names(data), 
                    function(x) 
                      (x %in% c(
                        dvs,
                        names(df.clean),  # Those already used
                        data %>% select(ends_with('updated')) %>% names(), # Those already used and renamed
                        data %>% select(starts_with('age_')) %>% names(), # Age column was consolidated
                        data %>% select(starts_with('Missing_')) %>% names(), # Missing columns aren't really necessary
                        do.call(paste, c(expand.grid(BE_cols.std, BE_suffixes), sep='_')),
                        'hh_cbsa_name', # this is renamed
                        # Add in thous
                        paste0(do.call(paste, c(expand.grid(BE_cols.std, BE_suffixes), sep='_')), '_thous'),
                        BE_cols.other
                      ))
                    )]


# 
do.call(paste, c(expand.grid(BE_cols.std, BE_suffixes), sep='_'))[do.call(paste, c(expand.grid(BE_cols.std, BE_suffixes), sep='_')) %>% 
                                                                    sapply(function(x) x %notin% names(data))] # "BusStopDens_half" "BusStopDens_one"  "NumBusStops_two"  "BusStopDens_two" 


# Assign
for(c in BE_cols.other) {
  df.clean[c] <- data[c]
}

# Check
BE_cols.std_expanded<- do.call(paste, c(expand.grid(BE_cols.std, BE_suffixes), sep='_'))


BE_cols.std_expanded[sapply(BE_cols.std_expanded, \(x) x %notin% names(df.clean))]
```

```{r CBSA code}
# CBSA Code
df.clean$cbsa_code <- data$hh_cbsa_updated
df.clean$cbsa_title <- setNames(cbsa_code_dict$cbsatitle, cbsa_code_dict$cbsacode)[df.clean$cbsa_code]

MAJOR_CBSAS <- c('SAC' = 40900, 'LA_OC' = 31080, 'SD' = 41740, 'SF_OAK' = 41860, 'IE' = 40140, 'SJ' = 41940)


df.clean$cbsa_consolidated <- if_else(df.clean$cbsa_code %in% MAJOR_CBSAS, set_names(names(MAJOR_CBSAS), MAJOR_CBSAS)[df.clean$cbsa_code], 'Other')

# Double Check
df.clean %>% select(cbsa_title, cbsa_consolidated) %>% table()
```

## Additional Columns
Mostly the missing values columns, but let's check whatever wasn't included already
```{r}


```

## Back Cleanup
Go back and look at the dataset as a whole to see what needs to be immediately removed

```{r dataset-cleanup}
# Replace dollar signs in the column names
df.clean <- df.clean %>% rename_with(\(x) str_replace(x, '\\$', ''))

# Scale data by 1000s
data %>% select(ends_with('thous'))
df.clean %>% 
  select(starts_with('PopDens'))

# Which have nulls
df.clean %>% 
  summarize(across(everything(), \(x) sum(is.na(x)))) %>%
  pivot_longer(everything()) %>%
  filter(value != 0) # Basically just hhincome, cbsa_title

# Now I want to see which columns didn't make it over
names(data)
```

# Record Selection
Choose which records to exclude outright - note: this section doesn't do anything, we are just exploring 
```{r record-filtering}
# Those with missing values
data %>% 
  summarize(across(starts_with('Missing'), sum)) %>% 
  pivot_longer(everything()) %>%
  arrange(value)

## Missing Age: 119
## Missing_HomeOwn: 11,

# Do any still have infinite values
data %>%
  summarize(across(everything(), \(x) any(is.infinite(x)))) %>%
  pivot_longer(everything()) %>%
  filter(value)
  
```

# Save File
```{r save-file}
df.clean %>% 
  write_csv('data/clean_df_for_modeling.csv')
```