---
title: "5.4 Example Modeling Process"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

# Sample Modeling Walkthrough
This is a fairly streamlined process that I have developed for this. It could all be a function itself but I think there's enough requirement for flexibility at specific steps - and not enough future use case - for it to just stay as is.

The goal is that you can just copy and paste this whole document and replace references to `sample.model` where necessary. This workflow will run the analysis, output modeling objects for further analysis and create the standard suite of 4 visualizations I've

I would bet some run-thrus may need a little hacking to work but the standard set of modeling outcomes should just work out of the box.

## Process Overview:
* Copy and paste, name your model (normally the next sequential number) and document what is different about this set

* Set the variables of interest for your model run

* Select your dataset, given these variables of interest, controls, any filtering 

*

```{r env}
library(tidyverse)
library(AER)
library(ggplot2)
library(scales)
library(rlang)
```

# (00) Model 00

- Document changes from previous model

## 00 - Data Prep
```{r model00 modeling setup}
# First set your demo controls. You can see in `5.2_modeling_setup.Rmd` that the 

demos.bucket_type <- 'open_ended' # one of c('discrete', 'continuous', 'open_ended')
demos.consolidate_vars <- FALSE # Use slimmer versions of columns

demo_controls.00 <- c(
  # Age 
  switch(demos.bucket_type, 
           discrete   = 'age_bucket',
           open_ended = expr(starts_with('age_OE')),
           continuous = 'age_est',
           NA
  ),
  # HH_Income
  switch(demos.bucket_type,
         discrete   = 'hhincome_cat',
         open_ended = expr(starts_with('hhincome_OE')),
         continuous = 'hhincome_est',
         NA
  ),
  'hhsize', 
  # Education
  switch(demos.bucket_type, 
         discrete   = 'education',
         open_ended = expr(starts_with('education_OE')), 
         continuous = 'education',
         NA),
  # Sex
  'sex' = if_else(demos.consolidate_vars, 'sex_consolidated', 'sex'), 
  # Race
  'race' = if_else(demos.consolidate_vars, 'race_consolidated', 'race'), 
  # Ethnicity
  'ethnicity',
  # Home_Ownership
  'homeown', 
  # Young Children
  'youngchildren',
  'cbsa' = 'cbsa_consolidated' # see 5.1 for definition of this
)

# List the built environment variables you might want
BE_vars.00 <- c('PopDens_two', 'RetDens_bg', 'distrail_walk_quarter', 'distrail_walk_one', 'NumBusStops_one', 'NetLoadDens_OX24_two', 'JobsWi45_transit_to_car_ratio',
                'JobsWithin45_Car', 
                'StreetDens_OX24_two', 'Missing_StreetDens_OX24_two'
                #'IntersectionDens_OX24_two', 'Missing_IntersectionDens_OX24_two',
)

#demo_quo <- quo(!!!demo_controls)
df.clean %>% select(!!!demo_controls.00)
```

## Pull dataset
```{r model00 pull dataset}
df.modeling00 <- 
  df.clean %>% 
  # <-  Add data filters here
  filter(
    vmt < 300 # , # 109
    #age_OE___NotMissing == 1, #119
    #homeown != 'Missing' # 136
  ) %>%
  # Create new columns/features here
  mutate(
    JobsWi45_transit_to_car_ratio = JobsWithin45_Transit/JobsWithin45_Car,
    has_youngchildren = if_else(youngchildren > 0, 1, 0),
    #PopDens_two = PopDens_two/1000,
    cbsa = if_else(cbsa_code %in% MAJOR_CBSAS, cbsa_code, 'Other'),
    major_cbsa = if_else(cbsa_code %in% MAJOR_CBSAS, 'major', 'minor')
  ) %>%
  # Select the columns you want (this is fairly standard)
  select(
    id,
    !!dv,
    !!!BE_vars.00, # Note: the !!!'s just de-reference the elements you created in the above chunk
    !!!demo_controls.00
  ) %>%
  # Fix it so that Missing is a separate category for HH-Income, Education
  mutate(
    hhincome___Missing = abs(1 - hhincome_OE___NotMissing),
    education___Missing = abs(1 - education_OE___NotMissing),
    age___Missing = abs(1 - age_OE___NotMissing),
  ) %>%
  # And finally remove those unneeded columns
  select(-hhincome_OE___NotMissing, -education_OE___NotMissing, -age_OE___NotMissing)
```

### 00 - Scaling
```{r model00 scaling}
# Save the scaling values and summaries for future
df.scalars.00 <- 
  df.modeling00 %>%
  select(!!!BE_vars.00) %>%
  summarize(across(
    everything(),
    .fns = c('mean' = mean, 'sd' = sd, 'quartile1' = \(x) quantile(x, .25), 'median' = median, 'quartile3' = \(x) quantile(x, .75)),
    .names = '{.col}___{.fn}'
  )) %>%
  pivot_longer(everything(), names_sep = '___', names_to = c('col', 'name')) %>%
  pivot_wider()
```


### 00 - Add Interaction terms
```{r model00 - add interaction terms}
# This is a small
get_summary_val <- function(var, metric, summary_tbl) {
  summary_tbl[[which(summary_tbl$col == var), metric]]
}

# 'loadDens_X_RetDens_above_med' = if NetLoadDens and Retail Density are both below the median
df.modeling00[['loadDens_X_RetDens_above_med']] <- if_else(
    (df.modeling00$NetLoadDens_OX24_two > get_summary_val('NetLoadDens_OX24_two', 'median', df.scalars.00)) &
      (df.modeling00$RetDens_bg > get_summary_val('RetDens_bg', 'median', df.scalars.00)),
    1,0)

# add the new columns to the column list if they should be there
BE_vars.00 <- c(BE_vars.00, 'loadDens_X_RetDens_above_med')
#demo_controls.00 <- c(demo_controls, '[NOTHING TO ADD HERE]')

# Repeat as necessary
```

## 00 - Scaling (pt. 2)
```{r model00 - scaling}
# Now Scale the BE-cols
BE_vars.00.to_scale <- c('PopDens_two', 'RetDens_bg', 'NetLoadDens_OX24_two', 'StreetDens_OX24_two','JobsWi45_transit_to_car_ratio', 'NumBusStops_one')

# sanity check
stopifnot(all(BE_vars.00.to_scale %in% BE_vars.00))

# scale vars
df.modeling00.scaled <- 
  df.modeling00 %>%
  mutate(across(
    !!BE_vars.00.to_scale,
    \(x) scale(x)[,1]
  ))
```


#### 00 - Model Setup & Run
```{r model00 model setup}
library(fastDummies)
# dummify
df.modeling00.dummies <- dummy_cols(df.modeling00.scaled, remove_selected_columns = TRUE, remove_most_frequent_dummy = FALSE)

names.00 <- df.modeling00.dummies %>% names()

# formula

# Set the base-vars, these are the baseline for the regression or default values upon which you add the coefficients. They will be removed from the dataset to avoid aliasing issues

# Note: These are the default columns you will use below in the modeling!
defaults_vars.00 <- 
  c('cbsa' = 'Other',
    'race' = 'White',
    'homeown' = 'Own',
    'sex' = 'Female',
    'ethnicity' = 'Non-Hispanic'
    )
vars_to_remove.00 <- purrr::imap_chr(defaults_vars.00, \(x, idx) paste0(idx, '_', x)) 

# Set Vars
vars.00 <- names.00[3:length(names.00)]
vars.00 <- vars.00[vars.00 %notin% vars_to_remove.00]

form.00 <- as.formula(paste(dv, '~', paste0(vars.00, collapse='+')))

# Model
model.00 <- AER::tobit(form.00, left=0, data=df.modeling00.dummies)

# Check Model output
summary(model.00)
# NOTE: If you get an issue with "aliased" variables when trying to view the summary, it means that some variables can be composed of others. Thus you need to remove one of them. 

# The test for aliasing is here - this will show you which columns are the problem, so either remove that one or the column that is equivalent that you'd prefer (e.g.)

which(is.na(coef(model.00))) # If you're fine, this will just be "named integer(0)"

# Save the raw output to an output file 
model.00 %>%
  tidy_tobit_model() %>%
  write_csv('output/model00_raw.csv')
```

## 00 - Analyze/Visualize Prep

To analyze the model build we can use the various built-in summary functions for AER::tobit but I am a visual learned so I built a couple wrappers over them to allow easier interpretation.

The process for doing this is a little janky and relies on a few custom functions. Essentially we'll create a 'Plotting DataFrame' via a standard process then plug that into a set of 3 plotting functions. These plotting functions are built to both run out of the box and be flexible (they have a lot of optional arguments) but all they do is create standard ggplot objects, so they can be modified directly be adding other ggplot layers like geoms, themes, labels, etc. with the standard `+`.

### 00 - Set Variable Titles 

First thing, we need to title the variables in your model to make them display how you want

This could be a lot cleaner but this works. You basically just format the strings by a series of cascading replacement strings here. If anything doesn't display correctly on the output, play around with these 

**Potential Pitfalls**
* some of these of course apply to multiple things so order does matter.
e.g. `'_', ' '` will replace all underscores with spaces so anything after that will need to reference spaces to work as intended

* be careful with special characters, for example, you need the `\\` before '$' otherwise it won't recognize it

### 
```{r model00 - set variable names}
new_names.00 <- 
  names(coef(model.00)) %>%
  # Distance Bands
  str_replace('_two', ' (2mi)') %>%
  str_replace('_one', ' (1mi)') %>%
  str_replace('_3quarter', ' (.75mi)') %>%
  str_replace('_one', ' (.5mi)') %>%
  str_replace('_3eighth', ' (.375mi)') %>%
  str_replace('_quarter', ' (.25mi)') %>%
  str_replace('_eighth', ' (.125mi)') %>%
  str_replace('_bg', ' (bg)') %>%
  # Open-Ended
  str_replace('hhincome_OE___', 'HH-Income: $') %>%
  str_replace('hhincome___', 'HH-Income: ') %>%
  str_replace('education_OE___', 'Education: ') %>%
  str_replace('education___', 'Education: ') %>%
  str_replace('age___', 'Age:') %>%
  str_replace('age_OE___', 'Age: ') %>%
  str_replace('\\$NotMissing', 'NotMissing') %>%
  str_replace('hhsize', 'HH-Size') %>%
  str_replace('OX24 ','') %>%
  str_replace('race', 'Race:') %>%
  str_replace('ethnicity', 'Ethnicity:') %>%
  str_replace('homeown', 'Home:') %>%
  str_replace('AI_Other_Multiple', 'AI/Other/Multiple') %>%
  str_replace('sex', 'Sex:') %>%
  # Constructed Vars
  str_replace('JobsWi45_transit_to_car_ratio', 'Jobs w/i 45min (transit to car)') %>%
  str_replace('loadDens_X_RetDens_above_med', 'LoadDens X RetDens > med') %>%
  str_replace_all('_', ' ') %>%
  #str_replace('and up', 'plus') %>%
  str_replace('\\$ ', ' $') %>%
  # Other
  str_replace('youngchildren TRUE', 'Has Young Children') %>%
  str_replace('youngchildren', '# Young Children') %>%
  str_replace('distrail walk', 'Has Rail Access Walk') %>%
  # CBSA
  str_replace('cbsa SF OAK', 'CBSA: San Francisco-Oakland') %>% 
  str_replace('cbsa SAC', 'CBSA: Sacramento') %>% 
  str_replace('cbsa LA OC', 'CBSA: Los Angeles/OC') %>% 
  str_replace('cbsa IE', 'CBSA: Riverside') %>% 
  str_replace('cbsa SJ', 'CBSA: San Jose') %>% 
  str_replace('cbsa SD', 'CBSA: San Diego') %>%
  I()
new_names.00 <- set_names(names(coef(model.00)), new_names.00)  
new_names.00

# Test output
model.00 %>%
  tidy_tobit_model() %>%
  filter(p.value < .05) %>%
  print(n = 26)
```

### Set up the plotting df
#### 00 - Setup Plotting DF
```{r model00 generate plot df}
# Create Plotting DF
model.00.pltdf <- 
  model.00 %>%
  tidy_tobit_model() %>% 
  # Add Stars
  mutate(
    signif_stars = 
      symnum(p.value,
       symbols   = c("***","**","*","·",""),
       cutpoints = p_cutpoints,
       corr      = FALSE
    ),
    signif_level = 
      symnum(p.value,
       symbols   = paste0('<' , tail(p_cutpoints, -1)),
       cutpoints = p_cutpoints, 
       corr      = FALSE
    ),
    # Set Display Names
    Term = if_else(is.na(set_names(names(new_names.00), new_names.00)[v]), v, set_names(names(new_names.00), new_names.00)[v]), # <-- uses `new_names00` from previous chunk
    grp = sapply(str_split(Term, ':'), \(x) x[[1]]), # <- first try just splitting on :
    ### CHECK HERE FOR ERRORS: this is sloppy
    grp = case_when(grp %in% c('Age','HH-Income','Education','Race','Ethnicity','Sex','CBSA','Home') ~ grp,
                    grp %in% c('# Young Children','HH-Size', 'Has Young Children') ~ 'Family',
                    grp %in% c('(Intercept)', 'Log(scale)') ~ 'Model',
                    .default = 'Built-Env.'),
    # Note: this levels argument determines the order the groups will display in
    grp = factor(grp, levels = c('Built-Env.','Model','Race','Ethnicity','Sex', 'Age','HH-Income','Education','Family','Home','CBSA')) 
  ) %>%
  select(grp, everything())

# Add in means and sds
var_summaries.00 <- 
  # Calculate mean and sd from the scaled table
  df.modeling00.dummies %>%
  select(-id, -vmt) %>%
  summarize(across(
    where(is.numeric),
    .fns = c('mean' = mean, 'sd' = sd),
    .names = '{.col}_____{.fn}'
  )) %>%
  pivot_longer(everything(), names_sep = '_____', names_to = c('col', 'name')) %>%
  pivot_wider() %>%
  # Now grab the prescaled values from the scalar df
  left_join(
    df.scalars.00,
    by = c('col'='col'),
    suffix = c('', '.prescaled')
  ) %>%
  mutate(
    # Here coalesce takes the prescaled value where it exists
    mean = coalesce(mean.prescaled, mean),
    sd = coalesce(sd.prescaled, sd)
  ) %>%
  select(-ends_with('.prescaled'))
  
# Now add the scaled data as additional columns
model.00.pltdf <-
  model.00.pltdf %>%
  left_join(
    var_summaries.00,
    by = c('v' = 'col')
  )

# Numericize the distance band into a column and then sort by it
BLOCK_GROUP_SENTINEL_VALUE <- '.001'
model.00.pltdf$dist_band<- model.00.pltdf$Term %>%
  str_replace('\\(bg\\)', paste0('(', BLOCK_GROUP_SENTINEL_VALUE, 'mi)')) %>%
  str_extract( '\\([^\\d]*(\\d+)[^\\d]*\\)') %>%
  str_replace('mi\\)','') %>%
  str_replace('\\(', '') %>%
  as.numeric()

model.00.pltdf <- 
  model.00.pltdf %>%
  arrange(grp, desc(dist_band))


model.00.pltdf <- 
  model.00.pltdf %>%
  mutate(grp2 = case_when(is.na(dist_band) ~ 'Other',
                          dist_band == as.numeric(BLOCK_GROUP_SENTINEL_VALUE) ~ 'Block Grp',
                          .default = paste0(scales::number(dist_band),'mi')
                )) %>%
    # Overwrite `grp` with `grp2`, use the levels argument to set the order you want things to display in
  mutate(dist_band_fct = factor(grp2, levels = c('2.00mi', '1.00mi','0.75mi','0.5mi','0.375mi','0.25mi','Block Grp','Other'))) %>%
  select(-grp2)

# Join in VIF
vif.00 <- tibble(var = names(car::vif(model.00)), vif=car::vif(model.00))

model.00.pltdf <-
  model.00.pltdf %>%
  inner_join(
    vif.00,
    'by' = c('v' = 'var')
  )

#View(model17.pltdf)
model.00.pltdf
```


### 00 -  Set Default Value
This sets the default value that will display in the charts. This is normally the largest group within a regression - its the group that was removed in the modeling section above
```{r model00 set default vals}
model.00.pltdf <- 
  model.00.pltdf %>% 
    mutate(
      default_val = case_when(
        grp == 'Built-Env.' ~ '', 
        grp == 'Ethnicity' ~ 'Non-Hispanic', 
        grp == 'Sex' ~ "Female", 
        grp %in% c('Age','HH-Income','Education') ~ "Not Missing", 
        grp == 'Race' ~ "White", 
        .default = "Other")) %>% 
    mutate(default_val = if_else(default_val == '', 
                                 'N/A', 
                                 paste0('[', default_val,']'))) %>% 
  select(grp, v, Term, default_val, everything())
```


### 00 - Visualize
```{r model00 all-std-viz}
# VIF Plot
### Fairly standard, internal so not much to mess around with
### Interpret: this plot will show you the degree of multi-collinearity in the regression. Anything over 5 is usually highly correlated with another variable (or set of variables) in the model and thus could be a potential candidate for exclusion
plot_vif(model.00.pltdf, title = 'Model 00: VIF')

# Corrplot
### Similar - internal so its a simple plot
BE_vars.00.names <- set_names(
  model.00.pltdf[model.00.pltdf$grp == 'Built-Env.', ]$v,
  model.00.pltdf[model.00.pltdf$grp == 'Built-Env.', ]$Term 
)
plot_corrplot(df.modeling00.dummies, vars_named = BE_vars.00.names, title = 'Model 00: CorrPlot')

# Coefs
model.00.pltdf %>% 
  plot_regression_coefs(remove_missing_flags = TRUE, title = 'Model 00 - Regression Coefficients (full)') + # for standard plots, not much to play around with
  theme( 
    # Increase font size
    strip.text = element_text(size = 14),
    panel.text = element_text(size = 14)
  )
  
# BE-Coefs
### - this one is a little more complicated
model.00.pltdf %>%
  # Filter to only those significant at the 10% level and only those in BE grp
  filter(
    p.value < .1,
    grp == 'Built-Env.'
    ) %>% 
  # Overwrite `grp` with `dist_band_fct`
  mutate(grp = dist_band_fct) %>%
  # Plot
  plot_regression_coefs(
    title = 'Model 00 - Regression Coefficients (BE)', # for BE, you want to change some of the input flags
    hide_nonprimary_grps = FALSE, display_summaries = FALSE, 
    add_labels=TRUE, add_demarcation_lines = FALSE, add_column_headers = FALSE
  ) +
  # Additional formatting
  facet_grid(grp~., scales='free', space='free_y', switch='y') + 
  theme(axis.text.y = element_text(size=14))
```
