---
title: "model31"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r env}
library(tidyverse)
library(AER)
library(ggplot2)
library(scales)
library(rlang)
```

# (31) Model 31

- Same as Model 28 but:
  - no over 75 category
  - add a interactive dummy if over 65 and under75k

## 31 - Data Prep
### Add fake Block Group ID to test for Std error clustering
```{r}
# We're gonna spoof the bg
bg_distinct_measures <- df.clean %>% distinct(across(ends_with('_bg')))
bg_distinct_measures$bg_fakeid <- paste0('bgfid_', seq.int(nrow(bg_distinct_measures)))

bgfid.JOIN_COLS <- head(names(bg_distinct_measures), -1)
names(bgfid.JOIN_COLS) <- bgfid.JOIN_COLS
bgfid.JOIN_COLS

# id_2_bgfid <- 
#   df.clean %>%
#   inner_join(
#     bg_distinct_measures,
#     by = bgfid.JOIN_COLS
#   ) %>%
#   select(id, bg_fakeid)

# Now join in
# df.clean <- 
#   df.clean %>%
#   inner_join(
#     id_2_bgfid,
#     by = 'id'
  # )
```

```{r model31 modeling setup}
# First set your demo controls. You can see in `5.2_modeling_setup.Rmd` that the 

demos.bucket_type <- 'open_ended' # one of c('discrete', 'continuous', 'open_ended')
demos.consolidate_vars <- FALSE # Use slimmer versions of columns

demo_controls.31 <- c(
  # Age 
  switch(demos.bucket_type, 
           discrete   = 'age_bucket',
           open_ended = expr(starts_with('age_OE')),
           continuous = 'age_est',
           NA
  ),
  # HH_Income
  switch(demos.bucket_type,
         discrete   = 'hhincome_cat',
         open_ended = expr(starts_with('hhincome_OE')),
         continuous = 'hhincome_est',
         NA
  ),
  'hhsize', 
  # Education
  switch(demos.bucket_type, 
         discrete   = 'education',
         open_ended = expr(starts_with('education_OE')), 
         continuous = 'education',
         NA),
  # Sex
  'sex' = if_else(demos.consolidate_vars, 'sex_consolidated', 'sex'), 
  # Race
  'race' = if_else(demos.consolidate_vars, 'race_consolidated', 'race'), 
  # Ethnicity
  'ethnicity',
  # Home_Ownership
  'homeown', 
  # Young Children
  'youngchildren',
  'cbsa' = 'cbsa_consolidated' # see 2.1 for definition of this
  
)

# List the built environment variables you might want
BE_vars.31 <- c('PopDens_two', 'RetDens_bg', 'distrail_walk_quarter', 'distrail_walk_one', 'NumBusStops_one', 'NetLoadDens_GF18_two', 'JobsWi45_transit_to_car_ratio', 
                #'NumBusStops_bg',
                'StreetDens_GF18_two' #'Missing_StreetDens_GF18_two'
                #'IntersectionDens_OX24_two', 'Missing_IntersectionDens_OX24_two',
)

#demo_quo <- quo(!!!demo_controls)
# Test
demo_controls.31

df.clean %>% select(!!!demo_controls.31)
```

## Pull dataset
```{r model31 pull dataset}
df.modeling31 <- 
  df.clean %>% 
  
  # <-  Record Selection
  filter(
    vmt < 300 # removed: 109 ppl
  ) %>%
  
  # Create new columns/features here
  mutate(
    JobsWi45_transit_to_car_ratio = JobsWithin45_Transit/JobsWithin45_Car,
    has_youngchildren = if_else(youngchildren > 0, 1, 0),
    major_cbsa = if_else(cbsa_code %in% MAJOR_CBSAS, 'major', 'minor'),
    # add new interaction term here
    ### NEW
    age_65plus_X_income_under75k = if_else((age_OE___65_and_up == 1) & (hhincome_OE____75k_and_up == 0) & (hhincome_OE___NotMissing == 1), 1, 0)
  ) %>%
  
  # Select the columns you want (this is fairly standard)
  select(
    id,
    !!dv,
    !!!BE_vars.31, # Note: the !!!'s just de-reference the elements you created in the above chunk
    !!!demo_controls.31,
    age_65plus_X_income_under75k,
    bg_fakeid
  ) %>%
  
  # Fix it so that Missing is a separate category for HH-Income, Education
  mutate(
    hhincome___Missing = abs(1 - hhincome_OE___NotMissing),
    education___Missing = abs(1 - education_OE___NotMissing),
    age___Missing = abs(1 - age_OE___NotMissing),
  ) %>%
  # And finally remove those unneeded columns
  select(
    -hhincome_OE___NotMissing, -education_OE___NotMissing, -age_OE___NotMissing,
    # add age columns
    -age_OE___75_and_up
  )

df.modeling31
```

### 31 - Scaling
```{r model31 scaling}
# Save the scaling values and summaries for future
df.scalars.31 <- 
  df.modeling31 %>%
  select(!!!BE_vars.31) %>%
  summarize(across(
    everything(),
    .fns = c('mean' = mean, 'sd' = sd, 'quartile1' = \(x) quantile(x, .25), 'median' = median, 'quartile3' = \(x) quantile(x, .75)),
    .names = '{.col}___{.fn}'
  )) %>%
  pivot_longer(everything(), names_sep = '___', names_to = c('col', 'name')) %>%
  pivot_wider()

df.scalars.31
```


### 31 - Add Interaction terms
```{r model31 - add interaction terms}
# This is a small helper function to make referencing the summary table from last chunk easier.
get_summary_val <- function(var, metric, summary_tbl) {
  summary_tbl[[which(summary_tbl$col == var), metric]]
}

# 'loadDens_X_RetDens_above_med' = if NetLoadDens and Retail Density are both above the median
df.modeling31[['loadDens_X_RetDens_above_med']] <- if_else(
    (df.modeling31$NetLoadDens_GF18_two > get_summary_val('NetLoadDens_GF18_two', 'median', df.scalars.31)) &
      (df.modeling31$RetDens_bg > get_summary_val('RetDens_bg', 'median', df.scalars.31)),
    1,0)

# loadDens_X_BusStops_below_thresh = if NetLoadDens Z < -.59 and NumBusStops_one < median
# NetLoadDens
Z.thresh.NetLoad <- -.5
thresh.NetLoad <- (Z.thresh.NetLoad * get_summary_val('NetLoadDens_GF18_two', 'sd', df.scalars.31)) +  get_summary_val('NetLoadDens_GF18_two', 'median', df.scalars.31)
thresh.NumBusStops <- get_summary_val('NumBusStops_one', 'mean', df.scalars.31)

df.modeling31[['loadDens_X_BusStops_below_thresh']] <- if_else(
  (df.modeling31$NetLoadDens_GF18_two < thresh.NetLoad) &
    (df.modeling31$NumBusStops_one < thresh.NumBusStops),
  1, 
  0
)

# add the new columns to the column list if they should be there
BE_vars.31 <- c(BE_vars.31, 'loadDens_X_RetDens_above_med', 'loadDens_X_BusStops_below_thresh')
```

## 31 - Scaling (pt. 2)
```{r model31 - scaling}
# Now Scale the BE-cols
BE_vars.31.to_scale <- c('PopDens_two', 'RetDens_bg', 'NetLoadDens_GF18_two', 'StreetDens_GF18_two','JobsWi45_transit_to_car_ratio', 'NumBusStops_one')

# sanity check
stopifnot(all(BE_vars.31.to_scale %in% BE_vars.31))

# scale vars
df.modeling31.scaled <- 
  df.modeling31 %>%
  mutate(across(
    !!BE_vars.31.to_scale,
    \(x) scale(x)[,1]  ## <- call standarize function on each column
  ))
```




#### 31 - Model Setup & Run
```{r model31 model setup}
library(fastDummies)
# dummify
df.modeling31.dummies <- fastDummies::dummy_cols(df.modeling31.scaled %>% select(-bg_fakeid), remove_selected_columns = TRUE, remove_most_frequent_dummy = FALSE)

names.31 <- df.modeling31.dummies %>% names()

# add the id back in
df.modeling31.dummies2 <- 
  df.modeling31.dummies %>%
  inner_join(
    id_2_bgfid,
    by = 'id'
  )

# Set the base-vars, these are the baseline for the regression or default values upon which you add the coefficients. They will be removed from the dataset to avoid aliasing issues

# Note: These are the default columns you will use below in the modeling!
defaults_vars.31 <- 
  c('cbsa' = 'Other',
    'race' = 'White',
    'homeown' = 'Own',
    'sex' = 'Female',
    'ethnicity' = 'Non-Hispanic'
    )

### 'cbsa' = 'Other' ----> 'cbsa_Other'
vars_to_remove.31 <- purrr::imap_chr(defaults_vars.31, \(x, idx) paste0(idx, '_', x)) 

# Set Vars
vars.31 <- names.31[3:length(names.31)]
vars.31 <- vars.31[vars.31 %notin% vars_to_remove.31]

form.31 <- as.formula(paste(dv, '~', paste0(vars.31, collapse='+')))

# Model
model.31 <- AER::tobit(
  form.31, 
  left=0, 
  data=df.modeling31.dummies2,
  robust = TRUE
)

# Check for clustering
sandwich::vcovCL(model.31, cluster = ~ bg_fakeid) # 
coeftest(model.31, vcov.=vcovCL(model.31, cluster=rownames(bgfid), type="HC0"))


# Check Model output
summary(model.31)
# NOTE: If you get an issue with "aliased" variables when trying to view the summary, it means that some variables can be composed of others. Thus you need to remove one of them. 

# The test for aliasing is here - this will show you which columns are the problem, so either remove that one or the column that is equivalent that you'd prefer (e.g.)

which(is.na(coef(model.31))) # If you're fine, this will just be "named integer(0)"

# Save the raw output to an output file 
model.31 %>%
  tidy_tobit_model() %>%
  write_csv('output/model31_raw.csv')

model.31 %>%
  tidy_tobit_model() %>%
  write_csv('models/model31/model31_raw.csv')
```

### Set Variable Names
```{r model31 - set variable names}
new_names.31 <- 
  names(coef(model.31)) %>%
  # Write out Race groups
  str_replace('AfAm', 'African-American') %>%
  str_replace('Asian', 'Asian') %>%
  str_replace('PI', 'Pacific Islander') %>%
  str_replace('Multi', 'Multiple Races') %>%
  # Distance Bands
  str_replace('_two', ' (2mi)') %>%
  str_replace('_one', ' (1mi)') %>%
  str_replace('_3quarter', ' (.75mi)') %>%
  str_replace('_one', ' (.5mi)') %>%
  str_replace('_3eighth', ' (.375mi)') %>%
  str_replace('_quarter', ' (.25mi)') %>%
  str_replace('_eighth', ' (.125mi)') %>%
  str_replace('_bg', ' (bg)') %>%
  # Open-Ended
  str_replace('hhincome_OE___', 'HH-Income: $') %>%
  str_replace('hhincome___', 'HH-Income: ') %>%
  str_replace('education_OE___', 'Education: ') %>%
  str_replace('education___', 'Education: ') %>%
  str_replace('age___', 'Age:') %>%
  str_replace('age_OE___', 'Age: ') %>%
  str_replace('\\$NotMissing', 'NotMissing') %>%
  str_replace('hhsize', 'HH-Size') %>%
  str_replace('OX24 ','') %>%
  str_replace('race', 'Race:') %>%
  str_replace('ethnicity', 'Ethnicity:') %>%
  str_replace('homeown', 'Home:') %>%
  str_replace('AI_Other_Multiple', 'AI/Other/Multiple') %>%
  str_replace('sex', 'Sex:') %>%
  # Constructed Vars
  str_replace('JobsWi45_transit_to_car_ratio', 'Jobs w/i 45min (transit to car)') %>%
  str_replace('loadDens_X_RetDens_above_med', 'LoadDens & RetDens > Med') %>%
  str_replace('loadDens_X_BusStops_below_thresh', 'LoadDens & BusStops < Treshhold') %>%
  str_replace('age_65plus_X_income_under75k', 'Interaction: Age 65+ & HH-income <$75k') %>%
  str_replace_all('_', ' ') %>%
  #str_replace('and up', 'plus') %>%
  str_replace('\\$ ', ' $') %>%
  # Other
  str_replace('youngchildren TRUE', 'Has Young Children') %>%
  str_replace('youngchildren', '# Young Children') %>%
  str_replace('distrail walk', 'Has Rail Access Walk') %>%
  # CBSA
  str_replace('cbsa SF OAK', 'CBSA: San Francisco-Oakland') %>% 
  str_replace('cbsa SAC', 'CBSA: Sacramento') %>% 
  str_replace('cbsa LA OC', 'CBSA: Los Angeles/OC') %>% 
  str_replace('cbsa IE', 'CBSA: Riverside') %>% 
  str_replace('cbsa SJ', 'CBSA: San Jose') %>% 
  str_replace('cbsa SD', 'CBSA: San Diego') %>%
  I()
new_names.31 <- set_names(names(coef(model.31)), new_names.31)
new_names.31

# Test output
model.31 %>%
  tidy_tobit_model() %>%
  filter(p.value < .05) %>%
  print(n = 26)
```

### Set up the plotting df
#### 31 - Setup Plotting DF
```{r model31 generate plot df}
# Create Plotting DF
model.31.pltdf <- 
  model.31 %>%
  tidy_tobit_model() %>% 
  # Add Stars
  mutate(
    signif_stars = 
      symnum(p.value,
       symbols   = c("***","**","*","·",""),
       cutpoints = p_cutpoints,
       corr      = FALSE
    ),
    signif_level = 
      symnum(p.value,
       symbols   = paste0('<' , tail(p_cutpoints, -1)),
       cutpoints = p_cutpoints, 
       corr      = FALSE
    ),
    # Set Display Names
    Term = if_else(is.na(set_names(names(new_names.31), new_names.31)[v]), v, set_names(names(new_names.31), new_names.31)[v]), # <-- uses `new_names25` from previous chunk
    grp = sapply(str_split(Term, ':'), \(x) x[[1]]), # <- first try just splitting on :
    ### CHECK HERE FOR ERRORS: this is sloppy
    grp = case_when(grp %in% c('Age','HH-Income','Education','Race','Ethnicity','Sex','CBSA','Home', 'Interaction') ~ grp,
                    grp %in% c('# Young Children','HH-Size', 'Has Young Children') ~ 'Family',
                    grp %in% c('(Intercept)', 'Log(scale)') ~ 'Model',
                    .default = 'Built-Env.'),
    # Note: this levels argument determines the order the groups will display in
    grp = factor(grp, levels = c('Built-Env.','Model','Race','Ethnicity','Sex', 'Age','HH-Income','Education','Family','Home','Interaction','CBSA')) 
  ) %>%
  select(grp, everything())

# Add in means and sds
var_summaries.31 <- 
  # Calculate mean and sd from the scaled table
  df.modeling31.dummies %>%
  select(-id, -vmt) %>%
  summarize(across(
    where(is.numeric),
    .fns = c('mean' = mean, 'sd' = sd),
    .names = '{.col}_____{.fn}'
  )) %>%
  pivot_longer(everything(), names_sep = '_____', names_to = c('col', 'name')) %>%
  pivot_wider() %>%
  # Now grab the prescaled values from the scalar df
  left_join(
    df.scalars.31,
    by = c('col'='col'),
    suffix = c('', '.prescaled')
  ) %>%
  mutate(
    # Here coalesce takes the prescaled value where it exists
    mean = coalesce(mean.prescaled, mean),
    sd = coalesce(sd.prescaled, sd)
  ) %>%
  select(-ends_with('.prescaled'))
  
# Now add the scaled data as additional columns
model.31.pltdf <-
  model.31.pltdf %>%
  left_join(
    var_summaries.31,
    by = c('v' = 'col')
  )

# Numericize the distance band into a column and then sort by it
BLOCK_GROUP_SENTINEL_VALUE <- '.001'
model.31.pltdf$dist_band<- model.31.pltdf$Term %>%
  str_replace('\\(bg\\)', paste0('(', BLOCK_GROUP_SENTINEL_VALUE, 'mi)')) %>%
  str_extract( '\\([^\\d]*(\\d+)[^\\d]*\\)') %>%
  str_replace('mi\\)','') %>%
  str_replace('\\(', '') %>%
  as.numeric()

model.31.pltdf <- 
  model.31.pltdf %>%
  arrange(grp, desc(dist_band))


model.31.pltdf <- 
  model.31.pltdf %>%
  mutate(grp2 = case_when(is.na(dist_band) ~ 'Other',
                          dist_band == as.numeric(BLOCK_GROUP_SENTINEL_VALUE) ~ 'Block Grp',
                          .default = paste0(scales::number(dist_band),'mi')
                )) %>%
    # Overwrite `grp` with `grp2`, use the levels argument to set the order you want things to display in
  mutate(dist_band_fct = factor(grp2, levels = c('2.00mi', '1.00mi','0.75mi','0.5mi','0.375mi','0.25mi','Block Grp','Other'))) %>%
  select(-grp2)

# Join in VIF
vif.31 <- tibble(var = names(car::vif(model.31)), vif=car::vif(model.31))

model.31.pltdf <-
  model.31.pltdf %>%
  inner_join(
    vif.31,
    'by' = c('v' = 'var')
  )

#View(model17.pltdf)
model.31.pltdf
```


### 31 -  Set Default Value
This sets the default value that will display in the charts. This is normally the largest group within a regression - its the group that was removed in the modeling section above
```{r model31 set default vals}
model.31.pltdf <- 
  model.31.pltdf %>% 
    mutate(
      default_val = case_when(
        grp == 'Built-Env.' ~ '', 
        grp == 'Ethnicity' ~ 'Non-Hispanic', 
        grp == 'Sex' ~ "Female", 
        grp %in% c('Age','HH-Income','Education') ~ "Not Missing", 
        grp == 'Race' ~ "White", 
        .default = "Other")) %>% 
    mutate(default_val = if_else(default_val == '', 
                                 'N/A', 
                                 paste0('[', default_val,']'))) %>% 
  select(grp, v, Term, default_val, everything())
```


### 31 - Visualize
```{r model31 all-std-viz}
# VIF Plot
### Fairly standard, internal so not much to mess around with
### Interpret: this plot will show you the degree of multi-collinearity in the regression. Anything over 5 is usually highly correlated with another variable (or set of variables) in the model and thus could be a potential candidate for exclusion
plot_vif(model.31.pltdf, title = 'Model 31 - VIF')

# Corrplot
### Similar - internal so its a simple plot
BE_vars.31.names <- set_names(
  model.31.pltdf[model.31.pltdf$grp == 'Built-Env.', ]$v,
  model.31.pltdf[model.31.pltdf$grp == 'Built-Env.', ]$Term 
)
plot_corrplot(df.modeling31.dummies, vars_named = BE_vars.31.names, title = 'Model 31 - CorrPlot')

# Coefs
model.31.pltdf %>% 
  plot_regression_coefs(remove_missing_flags = TRUE, title = 'Model 31 - Regression Coefficients (full)') + # for standard plots, not much to play around with
  theme( 
    # Increase font size
    strip.text = element_text(size = 14),
    panel.text = element_text(size = 14)
  )
  
# BE-Coefs
### - this one is a little more complicated
model.31.pltdf %>%
  # Filter to only those significant at the 10% level and only those in BE grp
  filter(
    p.value < .1,
    grp == 'Built-Env.'
    ) %>% 
  # Overwrite `grp` with `dist_band_fct`
  mutate(grp = dist_band_fct) %>%
  # Plot
  plot_regression_coefs(
    title = 'Model 31 - Regression Coefficients (BE)', # for BE, you want to change some of the input flags
    hide_nonprimary_grps = FALSE, display_summaries = FALSE, 
    add_labels=TRUE, add_demarcation_lines = FALSE, add_column_headers = FALSE
  ) +
  # Additional formatting
  facet_grid(grp~., scales='free', space='free_y', switch='y') + 
  theme(axis.text.y = element_text(size=14))
```

## 31 - Clustering on BG
```{r}
model31.clustered.vcovCL.out <- sandwich::vcovCL(model.31, cluster = ~ bg_fakeid) # 
model31.clustered.coeftest <- coeftest(model.31, vcovCL(model.31, cluster = ~ bg_fakeid)) # 
#coeftest(model.31, vcov.=vcovCL(model.31, cluster=rownames(bg_fakeid), type="HC0"))

model31.clustered.sandwich.out
model31.clustered.coeftest

# Running again with `coefci`
model31.CIs <- coefci(model.31, vcov = vcovCL, cluster = ~bg_fakeid)
model31.CIs

m1coeffs_with_clse

```